---
title             : "Distributions and Sampling Variance for Five Effect Size Measures of Variance Overlap"
shorttitle        : "Effect Size"
author: 
  - name          : "Erin M. Buchanan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "901 S. National Ave., Springfield, MO, 65897"
    email         : "erinbuchanan@missouristate.edu"
  - name          : "John E. Scofield"
    affiliation   : "2"
  - name          : "Arielle Cunningham"
    affiliation   : "1"
    
  - id            : "1"
    institution   : "Missouri State University"
  - id            : "2"
    institution   : "University of Missouri"

author_note: |
  Erin M. Buchanan is an Associate Professor of Quantitative Psychology at Missouri State University. John E. Scofield is a Ph.D. candidate in Cognitive Neuroscience at the University of Missouri. Arielle Cunningham is a masters candidate in the Experimental Psychology program at Missouri State University. All authors contributed equally to the creation of all parts of this manuscript. 

abstract: |


  
keywords          : "effect size, eta, omega, distribution, variance"

#bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
```

  Effect size measures play an integral role in the interpretation of empirical science, and are arguably one of the most important outcomes of inference testing [@Lakens2013]. Given an experimental manipulation, or an association between variables of interest, effect sizes yield a quantitative measure of the magnitude, strength, or importance of an effect [@Keppel2004; @Olejnik2003]. This is complementary to traditional null hypothesis significance testing (NHST), which cannot elucidate the size or importance of an effect of interest. While @Kirk2003 has noted the development of more than seventy effect size indices, the characteristics of many effect sizes still warrant further study.
  
  The majority of common effect size measures can be binned into two families: the *d* family, and the *r* family. The first, *d* type effect sizes, consist of mean differences between two groups [@Lakens2013; @Rosenthal1994]. These are often standardized (as with the popular Cohen's *d*). The *r* family deals with measures of association, or the amount of variance overlap. Variance overlap effect sizes are interpreted as proportions, which range from zero to one [@Maxwell2004]. Common examples of this type include eta squared, epsilon squared, and omega squared [@Hays1963; @Kelley1935; @Olejnik2000; @Pearson1905], which often accompany omnibus tests such as an analysis of variance (ANOVA). Effect sizes have been known to overestimate population effects. Eta squared has been shown to have a positive bias [@Olejnik2003; @Okada2013), resulting from its dependence with least-squares methods related to *t*-tests and ANOVA designs. Less biased versions such as omega squared and epsilon squared have been suggested, albeit are not bias free [@Okada2013; @Okada2016).

  Alongside inference testing, effect sizes are critical to a priori power analyses, as well as meta-analyses [@Keppel2004]. With the use of effect size indices, researchers can make better inferences about the magnitude and direction of effects in a given field of research. However, researchers need to address comparability problems associated with different types of effect size measures, as meta-analyses can be inconclusive unless the type of research design is considered and controlled for [@Okada2016]. Effect sizes can also be used from prior research when planning new studies. A-priori power analyses can provide suggested sample sizes given an effect in a field of research [@Lakens2013]. 
  
  While effect sizes from the *d* family have been well studied, and bias estimates have been of interest with variance overlap effect sizes, the distribution of common effect sizes have been relatively understudied, as most researchers assume they match the distribution of the test statistic. Therefore, *d* values are often calculated with *t*-tests because the formulas are mathematically similar (as *d* usually is only a transform of *t* by removing the square root of *N*). However, several researchers have shown that the distribution of *d* is not normal, and actually follows a non-central *t* distribution, even as the central limit theorem approximates normal for the sampling distribution of *t*.
  
  This study focuses on several related measures of variance overlap that are traditionally paired with ANOVA (linear models). Given that the calculation of confidence intervals should not be based on the normal approximation, and that meta-analytic techniques requiring variance estimation of effect size sampling distributions have been relatively unexplored, we utilized simulations to explore this topic. We first explore the distributions of five effect size measures of variance overlap, then explore the simulation of confidence intervals, and finally look at the simulation of sampling variances of effect size measures.


# Method

## Simulations

The focus of this study was commonly used variance overlap statistics and the following were calculated for each combination of the manipulated variables when appropriate: 1) $\eta^2$, 2) $\eta_p^2$, 3) $\omega^2$, 4) $\omega_p^2$, and 5) $\eta_G^2$. A complete formula sheet of the equations used to calculate these statistics can be found in our supplemental materials.  

The manipulated variables included sample size, study design type, effect size strength, correlation between levels, and number of levels. We generated datasets for each of the variable combinations by using the *mvtnorm* package in *R* [@Genz2017]. The data generated from this function are multivariate normal with specified variance and correlation between levels. The data was generated with mean values starting at *M* = 2.50 and increasing 0.50 points based on the number of levels (i.e., 2.50, 3.00, etc.). In order to simulate data a researcher might collect from participants, this data was transformed into Likert-style data by rounding to whole numbers and truncating data points to a one to seven range. To understand the effects of this procedure on effect sizes, please see @CITE-BIAS1. The emphasis in this paper is on the distribution of the effects, rather than effect size bias, and therefore, we wished to simulate a common set of data, as randomly generated data is often precise to 16 decimals, which is rarely true for data collected from human participants. Even when data is rounded, skew values still closely resembled a normal distribution.

Level sample size started at *n* = 20 and increased by *n* = 6 up to *n* = 110 participants. Between and within-subjects designs were simulated, include one- and two-way scenarios. The data was first generated at *n* per level. For the one-way designs, the levels were either analyzed as between or within subjects using the *ez* library with type three sum of squares [@Lawrence2017]. The two-way designs were created by generating a random set of *n* $\times$ levels data points and adding them to original data as a second independent variable. This variable was treated as either between or within subjects to create two-way designs (all between or within), and the original variable was treated as the variable of interest in the two-way design (i.e., effect sizes were not calculated for the random variable or the interaction). This procedure ensured that *n* per level was consistent across all simulations, although total *n* did increase for between-subject designs. 

Effect size strength was manipulated by changing the simulated variance per level small effects: $SD_^2$ = 5, medium effects: $SD^2$ = 3, and large effects: $SD^2$ = 1. The correlations between levels included the following values: 0, .1, .3, .5, .7, and .9. Last, the number of levels was manipluated at 3, 4, 5, and 6 levels. In total, 1152 cobminations (16 *n* by 3 effect size strength by 6 correlations by 4 levels) were simulated 1000 times each, resulting in nearly 1.2 million lines of data. The dataset was coded for manipulatd variables and includes degrees of freedom (df), sum of squares (SS), 
*F* values, *p* values, and $eta_G^2$ for each design combination, which is provided online. Therefore, across 1.2 million simulations, nearly 23 million effect sizes were generated (1.2 by 4 designs by 5 effect size measures). Not all values are investigated here, as many were nearly identical, but the Shiny application provided for visualization purposes allows any interested person to view each combination individually. Additionally, we used the *papaja* package to write this manuscript inline with our *R* syntax for transparency of procedure [@Aust2017]. 

NEED TO MAKE FORMULA SHEET 

```{r simulation-code, eval=FALSE, include=FALSE}
####simulations for data####
library(mvtnorm)
library(ez)
library(reshape)
##rmvnorm(n, mean = rep(0, nrow(sigma)), sigma = diag(length(mean)),
##        method=c("eigen", "svd", "chol"), pre0.9_9994 = FALSE)

####things to simulate####
##rotate around N values start at 20 in each level, then add 6 as you go
##keep means steady 2.5, 3, 3.5, etc.
##rotate around the number of levels 3-6
##rotate around SDs making eta small medium large
##rotate around correlated error 0, .1, 3., .5, .7, .9

####create blank data from for data####
totalsims = 1152*1000
mydata = data.frame(N = 1:totalsims)

####keep track of the simulation rounds####
round = 0

####loop over N values here####
##loop a
Nloops = seq(20, 110, 6)
for (a in 1:length(Nloops)) {
  
simulate = 0

####loop over M and levels values here####
##this loop will give you different numbers of means for the different number of levels
##loops b
levels = 3:6 

for (b in 1:length(levels)) {

topmean = c(3.5, 4.0, 4.5, 5)  
Means = seq(2.5, topmean[b], .5)


####loop over SD values here####
##loop c
SDloops = c(5, 3, 1)

for (c in 1:length(SDloops)) {

####loop over correlations here####
##loop d
corloops = c(0, .1, .3, .5, .7, .9)

for (d in 1:length(corloops)) {

####simulate 1000 rounds of data####

for (e in 1:1000) {
      ####make the data here####
      ##here we are going to want to make the cor / SD matrix pattern
      ##but that will depends on the number of levels 
      ##might have to do it by if statements? not very elegant

      if(levels[b] == 3) {
      sigma = matrix(c(SDloops[c],corloops[d],corloops[d],
                       corloops[d],SDloops[c],corloops[d],
                       corloops[d],corloops[d],SDloops[c]), nrow = 3, ncol = 3)
      }

      if(levels[b] == 4) {
      sigma = matrix(c(SDloops[c],corloops[d],corloops[d],corloops[d],
                   corloops[d],SDloops[c],corloops[d],corloops[d],
                   corloops[d],corloops[d],SDloops[c],corloops[d],
                   corloops[d],corloops[d],corloops[d],SDloops[c]), nrow = 4, ncol = 4)
      }

      if(levels[b] == 5) {
      sigma = matrix(c(SDloops[c],corloops[d],corloops[d],corloops[d],corloops[d],
                   corloops[d],SDloops[c],corloops[d],corloops[d],corloops[d],
                   corloops[d],corloops[d],SDloops[c],corloops[d],corloops[d],
                   corloops[d],corloops[d],corloops[d],SDloops[c],corloops[d],
                   corloops[d],corloops[d],corloops[d],corloops[d],SDloops[c]), nrow = 5, ncol = 5)
      }

      if(levels[b] == 6) {
      sigma = matrix(c(SDloops[c],corloops[d],corloops[d],corloops[d],corloops[d],corloops[d],
                   corloops[d],SDloops[c],corloops[d],corloops[d],corloops[d],corloops[d],
                   corloops[d],corloops[d],SDloops[c],corloops[d],corloops[d],corloops[d],
                   corloops[d],corloops[d],corloops[d],SDloops[c],corloops[d],corloops[d],
                   corloops[d],corloops[d],corloops[d],corloops[d],SDloops[c],corloops[d],
                   corloops[d],corloops[d],corloops[d],corloops[d],corloops[d],SDloops[c]), nrow = 6, ncol = 6)
      }
    
      dataset = rmvnorm(Nloops[a], Means, sigma)
      
      ##here we are simulating 1-7 Likert type data
      ##take off the digits
      ##take out the out of range values
      dataset = round(dataset, digits = 0)
      dataset[ dataset < 1 ] = 1
      dataset[ dataset > 7 ] = 7
      
      ####put in the basic statistics here####
      round = round + 1
      simulate = simulate + 1
      mydata$N[round] = Nloops[a]
      mydata$levels[round] = levels[b]
      mydata$stdev[round] = SDloops[c]
      mydata$correl[round] = corloops[d]
      mydata$simnum[round] = simulate
    
      ####begin RM ANOVA one way####
      dataset = as.data.frame(dataset)
      dataset$partno = as.factor(1:nrow(dataset))
      longdataset = melt(dataset,
                         id = "partno",
                         measured = colnames(longdataset[1:(ncol(longdataset)-1), ]))
      
      rmoutput = ezANOVA(data = longdataset,
                         wid = partno,
                         within = variable,
                         dv = value,
                         type = 3, 
                         detailed = T)
      
      mydata$RM1.dfm[round] = rmoutput$ANOVA$DFn[2]
      mydata$RM1.dfr[round] = rmoutput$ANOVA$DFd[2]
      mydata$RM1.ssm.p[round] = rmoutput$ANOVA$SSn[1]
      mydata$RM1.ssm.main[round] = rmoutput$ANOVA$SSn[2]
      mydata$RM1.ssr.p[round] = rmoutput$ANOVA$SSd[1]
      mydata$RM1.ssr.main[round] = rmoutput$ANOVA$SSd[2]
      mydata$RM1.F[round] = rmoutput$ANOVA$F[2]
      mydata$RM1.ges[round] = rmoutput$ANOVA$ges[2]
            
      ####begin RM ANOVA two way####
      tempstuff = longdataset
      randomvalues = rnorm(Nloops[a], mean(Means), 1)
      tempstuff$value = tempstuff$value + randomvalues
      
      tempstuff$value = round(tempstuff$value, digits = 0)
      tempstuff$value[  tempstuff$value < 1 ] = 1
      tempstuff$value[  tempstuff$value > 7 ] = 7
      
      doublermdata = rbind(longdataset, tempstuff)
      
      level1 = as.numeric(gl(2, Nloops[a]/2, nrow(longdataset), labels = c("1", "2")))
      level2 = 3 - as.numeric(gl(2, Nloops[a]/2, nrow(longdataset), labels = c("2", "1")))
      
      doublermdata$rmlevel2 = as.factor(c(level1,level2))
      
      rmoutput2 = ezANOVA(data = doublermdata,
                            wid = partno,
                            within = .(variable, rmlevel2),
                            dv = value,
                            type = 3,
                            detailed = T)
      
      mydata$RM2.dfm[round] = rmoutput2$ANOVA$DFn[2]
      mydata$RM2.dfr[round] = rmoutput2$ANOVA$DFd[2]
      mydata$RM2.ssm.p[round] = rmoutput2$ANOVA$SSn[1]
      mydata$RM2.ssm.main[round] = rmoutput2$ANOVA$SSn[2]
      mydata$RM2.ssm.other[round] = rmoutput2$ANOVA$SSn[3]
      mydata$RM2.ssm.interact[round] = rmoutput2$ANOVA$SSn[4]
      mydata$RM2.ssr.p[round] = rmoutput2$ANOVA$SSd[1]
      mydata$RM2.ssr.main[round] = rmoutput2$ANOVA$SSd[2]
      mydata$RM2.ssr.other[round] = rmoutput2$ANOVA$SSd[3]
      mydata$RM2.ssr.interact[round] = rmoutput2$ANOVA$SSd[4]
      mydata$RM2.F[round] = rmoutput2$ANOVA$F[2]
      mydata$RM2.ges[round] = rmoutput2$ANOVA$ges[2]
      
      ####begin MIXED ANOVA two way####
      longdataset$level2 = gl(2, Nloops[a]/2, nrow(longdataset), labels = c("level 1", "level 2"))
      
      mixedoutput = ezANOVA(data = longdataset,
                          wid = partno,
                          within = variable,
                          between = level2,
                          dv = value,
                          type = 3,
                          detailed = T)
      
      mydata$MIX.dfm[round] = mixedoutput$ANOVA$DFn[3]
      mydata$MIX.dfr[round] = mixedoutput$ANOVA$DFd[3]
      mydata$MIX.ssm.p[round] = mixedoutput$ANOVA$SSn[1]
      mydata$MIX.ssm.other[round] = mixedoutput$ANOVA$SSn[2]
      mydata$MIX.ssm.main[round] = mixedoutput$ANOVA$SSn[3]
      mydata$MIX.ssm.interact[round] = mixedoutput$ANOVA$SSn[4]
      mydata$MIX.ssr.p[round] = mixedoutput$ANOVA$SSd[1]
      mydata$MIX.ssr.other[round] = mixedoutput$ANOVA$SSd[2]
      mydata$MIX.ssr.main[round] = mixedoutput$ANOVA$SSd[3]
      mydata$MIX.ssr.interact[round] = mixedoutput$ANOVA$SSd[4]
      mydata$MIX.F[round] = mixedoutput$ANOVA$F[3]
      mydata$MIX.ges[round] = mixedoutput$ANOVA$ges[3]
      
      ####begin BN ANOVA one way####
      longdataset$bnpartno = as.factor(1:nrow(longdataset))
      bnoutput = ezANOVA(data = longdataset,
                         wid = bnpartno,
                         between = variable,
                         dv = value, 
                         type = 3, 
                         detailed = T)
      
      mydata$BN1.dfm[round] = bnoutput$ANOVA$DFn[2]
      mydata$BN1.dfr[round] = bnoutput$ANOVA$DFd[2]
      mydata$BN1.ssm.p[round] = bnoutput$ANOVA$SSn[1]
      mydata$BN1.ssm.main[round] = bnoutput$ANOVA$SSn[2]
      mydata$BN1.ssr.p[round] = bnoutput$ANOVA$SSd[1]
      mydata$BN1.ssr.main[round] = bnoutput$ANOVA$SSd[2]
      mydata$BN1.F[round] = bnoutput$ANOVA$F[2]
      mydata$BN1.ges[round] = bnoutput$ANOVA$ges[2]
       
      ####begin BN ANOVA two way####
      bnoutput2 = ezANOVA(data = longdataset,
                            wid = bnpartno,
                            between = .(variable, level2),
                            dv = value,
                            type = 3,
                            detailed = T)

      mydata$BN2.dfm[round] = bnoutput2$ANOVA$DFn[2]
      mydata$BN2.dfr[round] = bnoutput2$ANOVA$DFd[2]
      mydata$BN2.ssm.p[round] = bnoutput2$ANOVA$SSn[1]
      mydata$BN2.ssm.main[round] = bnoutput2$ANOVA$SSn[2]
      mydata$BN2.ssm.other[round] = bnoutput2$ANOVA$SSn[3]
      mydata$BN2.ssm.interact[round] = bnoutput2$ANOVA$SSn[4]
      mydata$BN2.ssr.all[round] = bnoutput2$ANOVA$SSd[1]
      mydata$BN2.F[round] = bnoutput2$ANOVA$F[2]
      mydata$BN2.ges[round] = bnoutput2$ANOVA$ges[2]
      
} ##end sim loop

  
  filename = paste(round, ".csv", sep = "")
  datalines = (abs(round-999):round)
  write.csv(mydata[ datalines, ], file = filename)
  
      
} ##end N loop

} ##end levels loop

} ##end SD loop

} ##end cor loop

```

```{r data-setup, include = FALSE}

fulldata = read.csv("fulldata.csv")

#calculate partial eta squared
fulldata$RM1.pes = fulldata$RM1.ssm.main / (fulldata$RM1.ssm.main + fulldata$RM1.ssr.main)
fulldata$RM2.pes = fulldata$RM2.ssm.main / (fulldata$RM2.ssm.main + fulldata$RM2.ssr.main)
fulldata$MIX.pes = fulldata$MIX.ssm.main / (fulldata$MIX.ssm.main + fulldata$MIX.ssr.main)
fulldata$BN1.pes = fulldata$BN1.ssm.main / (fulldata$BN1.ssm.main + fulldata$BN1.ssr.main)
fulldata$BN2.pes = fulldata$BN2.ssm.main / (fulldata$BN2.ssm.main + fulldata$BN2.ssr.all)

#calculate full eta squared
fulldata$RM1.fes = fulldata$RM1.ssm.main / (fulldata$RM1.ssm.main + fulldata$RM1.ssr.main + fulldata$RM1.ssr.p)
fulldata$RM2.fes = fulldata$RM2.ssm.main / 
  (fulldata$RM2.ssm.main + fulldata$RM2.ssr.main + fulldata$RM2.ssm.other + fulldata$RM2.ssm.interact + fulldata$RM2.ssr.p + fulldata$RM2.ssr.other + fulldata$RM2.ssr.interact)
fulldata$MIX.fes = fulldata$MIX.ssm.main / 
  (fulldata$MIX.ssm.main + fulldata$MIX.ssr.main + fulldata$MIX.ssm.other + fulldata$MIX.ssm.interact + fulldata$MIX.ssr.p + fulldata$MIX.ssr.other + fulldata$MIX.ssr.interact)
fulldata$BN1.fes = fulldata$BN1.ssm.main / (fulldata$BN1.ssm.main + fulldata$BN1.ssr.main)
fulldata$BN2.fes = fulldata$BN2.ssm.main / (fulldata$BN2.ssm.main + fulldata$BN2.ssr.all + fulldata$BN2.ssm.other + fulldata$BN2.ssm.interact)

#calculate full omega squared
fulldata$RM1.fos = (fulldata$RM1.dfm*((fulldata$RM1.ssm.main/fulldata$RM1.dfm)-(fulldata$RM1.ssr.main/fulldata$RM1.dfr)))/
  ((fulldata$RM1.ssm.main+fulldata$RM1.ssr.main+fulldata$RM1.ssr.p)+(fulldata$RM1.ssm.p/(fulldata$RM1.dfr/fulldata$RM1.dfm)))
fulldata$RM2.fos = (fulldata$RM2.dfm*((fulldata$RM2.ssm.main/fulldata$RM2.dfm)-(fulldata$RM2.ssr.main/fulldata$RM2.dfr)))/
  ((fulldata$RM2.ssm.main+fulldata$RM2.ssr.main+fulldata$RM2.ssm.other+fulldata$RM2.ssr.other+fulldata$RM2.ssm.interact+fulldata$RM2.ssr.interact+fulldata$RM2.ssr.p)+(fulldata$RM2.ssm.p/(fulldata$RM2.dfr/fulldata$RM2.dfm)))
fulldata$MIX.fos = (fulldata$MIX.dfm*((fulldata$MIX.ssm.main/fulldata$MIX.dfm)-(fulldata$MIX.ssr.main/fulldata$MIX.dfr)))/
  (fulldata$MIX.ssm.main+fulldata$MIX.ssr.main+fulldata$MIX.ssr.p+(fulldata$MIX.ssr.main/(fulldata$MIX.dfr/fulldata$MIX.dfm)))
fulldata$BN1.fos = (fulldata$BN1.dfm*((fulldata$BN1.ssm.main/fulldata$BN1.dfm)-(fulldata$BN1.ssr.main/fulldata$BN1.dfr)))/
  ((fulldata$BN1.ssm.main + fulldata$BN1.ssr.main)+(fulldata$BN1.ssr.main/fulldata$BN1.dfr))
fulldata$BN2.fos = (fulldata$BN2.dfm*((fulldata$BN2.ssm.main/fulldata$BN2.dfm)-(fulldata$BN2.ssr.all/fulldata$BN2.dfr)))/
  ((fulldata$BN2.ssm.main + fulldata$BN2.ssr.all + fulldata$BN2.ssm.other + fulldata$BN2.ssm.interact)+(fulldata$BN2.ssr.all/fulldata$BN2.dfr))

#calculate partial omega squared
#RM1 NA
#BN1 NA
fulldata$RM2.pos = (fulldata$RM2.dfm*((fulldata$RM2.ssm.main/fulldata$RM2.dfm)-(fulldata$RM2.ssr.main/fulldata$RM2.dfr)))/
  (fulldata$RM2.ssm.main+fulldata$RM2.ssr.main+fulldata$RM2.ssr.p+(fulldata$RM2.ssr.p/(fulldata$RM2.dfr/fulldata$RM2.dfm)))
fulldata$BN2.pos = (fulldata$BN2.dfm*((fulldata$BN2.ssm.main/fulldata$BN2.dfm)-(fulldata$BN2.ssr.all/fulldata$BN2.dfr)))/
  (fulldata$BN2.ssm.main+(((fulldata$N*fulldata$levels)-fulldata$BN2.dfm)*(fulldata$BN2.ssr.all/fulldata$BN2.dfr)))
fulldata$MIX.pos = (fulldata$MIX.dfm*((fulldata$MIX.ssm.main/fulldata$MIX.dfm)-(fulldata$MIX.ssr.main/fulldata$MIX.dfr)))/
  (fulldata$MIX.ssm.main+fulldata$MIX.ssr.main+fulldata$MIX.ssr.p+(fulldata$MIX.ssr.p/(fulldata$MIX.dfr/fulldata$MIX.dfm)))

####look at values to see how they compare####
names(fulldata)
justes = fulldata[ , c(15, 27, 39, 47, 56:74)]
cor(justes[ , 1:5]) ##rm1, mix, bn1, bn2 versus rm2 GES 
cor(justes[ , 6:10]) ##rm1, rm2, mix versus bn1/bn2 PES
cor(justes[ , 11:15]) ##rm1, mix, bn1, bn2 versus rm2 FES
cor(justes[ , 16:20]) ##rm1, mix, bn1, bn2 versus rm2 FOS
cor(justes[ , 21:23]) ##all perfectly correlated, use RM2 POS

fulldata$popeta = NA
fulldata$popeta[ fulldata$levels == 3 & fulldata$stdev == 5] = 0.03225806
fulldata$popeta[ fulldata$levels == 3 & fulldata$stdev == 3] = 0.05263158
fulldata$popeta[ fulldata$levels == 3 & fulldata$stdev == 1] = 0.14285714
fulldata$popeta[ fulldata$levels == 4 & fulldata$stdev == 5] = 0.05882353
fulldata$popeta[ fulldata$levels == 4 & fulldata$stdev == 3] = 0.09433962
fulldata$popeta[ fulldata$levels == 4 & fulldata$stdev == 1] = 0.23809524
fulldata$popeta[ fulldata$levels == 5 & fulldata$stdev == 5] = 0.09090909
fulldata$popeta[ fulldata$levels == 5 & fulldata$stdev == 3] = 0.14285714
fulldata$popeta[ fulldata$levels == 5 & fulldata$stdev == 1] = 0.33333333
fulldata$popeta[ fulldata$levels == 6 & fulldata$stdev == 5] = 0.12727270
fulldata$popeta[ fulldata$levels == 6 & fulldata$stdev == 3] = 0.19553070
fulldata$popeta[ fulldata$levels == 6 & fulldata$stdev == 1] = 0.42168670

fulldata$ncp = fulldata$popeta / ((1-fulldata$popeta)*(fulldata$N * fulldata$levels))

```

```{r graphs}

library(ggplot2)

cleanup = theme(panel.grid.major = element_blank(), 
                panel.grid.minor = element_blank(), 
                panel.background = element_blank(), 
                axis.line.x = element_line(color = "black"),
                axis.line.y = element_line(color = "black"),
                legend.key = element_rect(fill = "white"),
                text = element_text(size = 14))

##use all RM2
#N = 110
#correl = 0
#across all levels with color

smalldata = subset(fulldata, stdev == 5 & correl == 0 & N == 110)
meddata = subset(fulldata, stdev == 3 & correl == 0 & N == 110)
largedata = subset(fulldata, stdev == 1 & correl == 0 & N == 110)

smalldata$levels = as.factor(smalldata$levels)
meddata$levels = as.factor(meddata$levels)
largedata$levels = as.factor(largedata$levels)

####make small effect size histograms####
histGESsmall = ggplot(smalldata, aes(RM2.ges, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  ggtitle("Small Effects") + 
  ylab("Generalized Effect Size") +
  xlab(" ") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b")) + 
  coord_cartesian(xlim = c(0,.30), ylim = c(0,400))
 
histFESsmall = ggplot(smalldata, aes(RM2.fes, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  xlab("Full Eta Squared") + 
  ylab("Frequency") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b"))

histPOSsmall = ggplot(smalldata, aes(RM2.pos, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  xlab(" ") + 
  ylab("Partial Omega Squared") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b")) +
  coord_cartesian(xlim = c(0,.30), ylim = c(0,200))

histFOSsmall = ggplot(smalldata, aes(RM2.fos, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  xlab("Full Omega Squared") + 
  ylab("Frequency") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b"))

histPESsmall = ggplot(smalldata, aes(RM2.pes, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  xlab(" ") + 
  ylab("Partial Eta Squared") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b")) + 
  coord_cartesian(xlim = c(0,.30), ylim = c(0,200))

####make medium size histograms####
histGESmed = ggplot(meddata, aes(RM2.ges, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  ggtitle("Medium Effects") + 
  ylab(" ") +
  xlab(" ") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b")) +
  coord_cartesian(xlim = c(0,.35), ylim = c(0,400))

histFESmed = ggplot(meddata, aes(RM2.fes, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  xlab("Full Eta Squared") + 
  ylab("Frequency") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b"))

histPOSmed = ggplot(meddata, aes(RM2.pos, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  xlab(" ") + 
  ylab(" ") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b")) +
  coord_cartesian(xlim = c(0,.35), ylim = c(0,200))

histFOSmed = ggplot(meddata, aes(RM2.fos, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  xlab("Full Omega Squared") + 
  ylab("Frequency") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b"))

histPESmed = ggplot(meddata, aes(RM2.pes, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  xlab(" ") + 
  ylab(" ") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b")) +
  coord_cartesian(xlim = c(0,.35), ylim = c(0,200))

####make large effect histograms####
histGESlarge = ggplot(largedata, aes(RM2.ges, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  ggtitle("Large Effects") + 
  ylab(" ") +
  xlab(" ") + 
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b")) +
  coord_cartesian(xlim = c(0,.55), ylim = c(0,400)) 

histFESlarge = ggplot(largedata, aes(RM2.fes, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  xlab("Full Eta Squared") + 
  ylab("Frequency") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b"))

histPOSlarge = ggplot(largedata, aes(RM2.pos, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  xlab(" ") + 
  ylab(" ") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b")) +
  coord_cartesian(xlim = c(0,.55), ylim = c(0,200))

histFOSlarge = ggplot(largedata, aes(RM2.fos, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  xlab("Full Omega Squared") + 
  ylab("Frequency") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b"))

histPESlarge = ggplot(largedata, aes(RM2.pes, fill = levels)) + 
  geom_histogram(binwidth = .005) +
  cleanup + 
  xlab(" ") + 
  ylab(" ") +
  scale_fill_manual(name = "Levels", 
                    values = c("#450000", "#0e1a40", "#1d1485", "#52506b")) +
  coord_cartesian(xlim = c(0,.55), ylim = c(0,200))

library(cowplot)
legend = get_legend(histGESsmall)

ninesquare <- plot_grid( histGESsmall + theme(legend.position="none"),
                   histGESmed + theme(legend.position="none"),
                   histGESlarge + theme(legend.position="none"),
                   histPESsmall + theme(legend.position="none"),
                   histPESmed + theme(legend.position="none"),
                   histPESlarge + theme(legend.position="none"),
                   histPOSsmall + theme(legend.position="none"),
                   histPOSmed + theme(legend.position="none"),
                   histPOSlarge + theme(legend.position="none"),
                   hjust = -1,
                   nrow = 3)

tiff(filename = "ninesquare.tiff", res = 300, width = 8, 
     height = 8, units = 'in', compression = "lzw")
plot(ninesquare)
dev.off()

```

```{r distribution-estimation, eval=FALSE, include=FALSE}

####ges rm1 versus rm2####
library(fitdistrplus)
round = 0
distributiondata = data.frame(N = 1:1152)

##loop a over N
Nloops = seq(20, 110, 6)
for (a in 1:length(Nloops)) {
  ##loops b over levels
  levelloop = 3:6 
  for (b in 1:length(levelloop)) {
    ##loop c over effect size
    SDloops = c(5, 3, 1)
    for (c in 1:length(SDloops)) {
    ##loop d over correlation
      corloops = c(0, .1, .3, .5, .7, .9)
      for (d in 1:length(corloops)) {
        
        dataset = subset(fulldata,
                         N == Nloops[a] &
                           levels == levelloop[b] &
                           stdev == SDloops[c] &
                           correl == corloops[d])
        
        round = round + 1
        distributiondata$N[round] = Nloops[a]
        distributiondata$levels[round] = levelloop[b]
        distributiondata$stdev[round] = SDloops[c]
        distributiondata$correl[round] = corloops[d]
        
        ##don't work with zeroes
        dataset2 = subset(dataset, RM1.ges > 0)
        dataset3 = subset(dataset, RM2.ges > 0)
        
        ##normal distribution
        normaloutput = fitdist(dataset2$RM1.ges, "norm", keepdata = T)
        normaloutput2 = fitdist(dataset3$RM2.ges, "norm", keepdata = T)
        distributiondata$norm.1.aic[round] = normaloutput$aic
        distributiondata$norm.1.mean[round] = normaloutput$estimate[1]
        distributiondata$norm.1.sd[round] = normaloutput$estimate[2]
        distributiondata$norm.2.aic[round] = normaloutput2$aic
        distributiondata$norm.2.mean[round] = normaloutput2$estimate[1]
        distributiondata$norm.2.stdev[round] = normaloutput2$estimate[2]
        
        ##exponential
        expoutput = fitdist(dataset2$RM1.ges, "exp", keepdata = T)
        expoutput2 = fitdist(dataset3$RM2.ges, "exp", keepdata = T)
        distributiondata$exp.1.aic[round] = expoutput$aic
        distributiondata$exp.1.rate[round] = expoutput$estimate
        distributiondata$exp.2.aic[round] = expoutput2$aic
        distributiondata$exp.2.rate[round] = expoutput2$estimate
        
        ##gamma
        gammaoutput = fitdist(dataset2$RM1.ges, "gamma", lower = c(0,0), start = list(shape = 1.0, rate = 5), keepdata = T)
        gammaoutput2 = fitdist(dataset3$RM2.ges, "gamma", lower = c(0,0), start = list(shape = 1.0, rate = 5), keepdata = T)
        distributiondata$gamma.1.aic[round] = gammaoutput$aic
        distributiondata$gamma.1.shape[round] = gammaoutput$estimate[1]
        distributiondata$gamma.1.rate[round] = gammaoutput$estimate[2]
        distributiondata$gamma.2.aic[round] = gammaoutput2$aic
        distributiondata$gamma.2.shape[round] = gammaoutput2$estimate[1]
        distributiondata$gamma.2.rate[round] = gammaoutput2$estimate[2]
        
        ##log normal
        lognormoutput = fitdist(dataset2$RM1.ges, "lnorm", keepdata = T)
        lognormoutput2 = fitdist(dataset3$RM2.ges, "lnorm", keepdata = T)
        distributiondata$lnorm.1.aic[round] = lognormoutput$aic
        distributiondata$lnorm.1.mean[round] = lognormoutput$estimate[1]
        distributiondata$lnorm.1.stdev[round] = lognormoutput$estimate[2]
        distributiondata$lnorm.2.aic[round] = lognormoutput2$aic
        distributiondata$lnorm.2.mean[round] = lognormoutput2$estimate[1]
        distributiondata$lnorm.2.stdev[round] = lognormoutput2$estimate[2]
        
        ##beta
        betaoutput = fitdist(dataset2$RM1.ges, "beta", keepdata = T)
        betaoutput2 = fitdist(dataset3$RM2.ges, "beta", keepdata = T)
        distributiondata$beta.1.aic[round] = betaoutput$aic
        distributiondata$beta.1.shape1[round] = betaoutput$estimate[1]
        distributiondata$beta.1.shape2[round] = betaoutput$estimate[2]
        distributiondata$beta.2.aic[round] = betaoutput2$aic
        distributiondata$beta.2.shape1[round] = betaoutput2$estimate[1]
        distributiondata$beta.2.shape2[round] = betaoutput2$estimate[2]
        
        ##chi square
        chioutput = fitdist(dataset2$RM1.ges, "chisq", start = list(df = 1))
        chioutput2 = fitdist(dataset3$RM2.ges, "chisq", start = list(df = 1))
        distributiondata$chi.1.aic[round] = chioutput$aic
        distributiondata$chi.1.df[round] = chioutput$estimate
        distributiondata$chi.2.aic[round] = chioutput2$aic
        distributiondata$chi.2.df[round] = chioutput2$estimate
        
        ##f
        foutput = fitdist(dataset2$RM1.ges, "f", keepdata = T, 
                          start = list(df1 = (dataset$RM1.dfm[1]), df2 = (dataset$RM1.dfr[1])), 
                          optim.method="SANN")
        foutput2 = fitdist(dataset3$RM2.ges, "f", keepdata = T, 
                           start = list(df1 = (dataset$RM2.dfm[1]), df2 = (dataset$RM2.dfr[1])), 
                           optim.method="SANN")
        distributiondata$f.1.aic[round] = foutput$aic
        distributiondata$f.1.df1[round] = foutput$estimate[1]
        distributiondata$f.1.df2[round] = foutput$estimate[2]
        distributiondata$f.2.aic[round] = foutput2$aic
        distributiondata$f.2.df1[round] = foutput2$estimate[1]
        distributiondata$f.2.df2[round] = foutput2$estimate[2]        

        ##logistic
        logoutput = fitdist(dataset2$RM1.ges, "logis", keepdata = T)
        logoutput2 = fitdist(dataset3$RM2.ges, "logis", keepdata = T)
        distributiondata$log.1.aic[round] = logoutput$aic
        distributiondata$log.1.loc[round] = logoutput$estimate[1]
        distributiondata$log.1.scale[round] = logoutput$estimate[2]
        distributiondata$log.2.aic[round] = logoutput2$aic
        distributiondata$log.2.loc[round] = logoutput2$estimate[1]
        distributiondata$log.2.scale[round] = logoutput2$estimate[2]
        
      }
    }
  }
}

write.csv(distributiondata, "ges_distribution.csv", row.names = F)

####pes rm1 versus bn1####
round = 0
distributiondata = data.frame(N = 1:1152)

##loop a over N
Nloops = seq(20, 110, 6)
for (a in 1:length(Nloops)) {
  ##loops b over levels
  levelloop = 3:6 
  for (b in 1:length(levelloop)) {
    ##loop c over effect size
    SDloops = c(5, 3, 1)
    for (c in 1:length(SDloops)) {
      ##loop d over correlation
      corloops = c(0, .1, .3, .5, .7, .9)
      for (d in 1:length(corloops)) {
        
        dataset = subset(fulldata,
                         N == Nloops[a] &
                           levels == levelloop[b] &
                           stdev == SDloops[c] &
                           correl == corloops[d])
        
        round = round + 1
        distributiondata$N[round] = Nloops[a]
        distributiondata$levels[round] = levelloop[b]
        distributiondata$stdev[round] = SDloops[c]
        distributiondata$correl[round] = corloops[d]
        
        ##don't work with zeroes
        dataset2 = subset(dataset, RM1.pes > 0)
        dataset3 = subset(dataset, BN1.pes > 0)
        
        ##normal distribution
        normaloutput = fitdist(dataset2$RM1.pes, "norm", keepdata = T)
        normaloutput2 = fitdist(dataset3$BN1.pes, "norm", keepdata = T)
        distributiondata$norm.1.aic[round] = normaloutput$aic
        distributiondata$norm.1.mean[round] = normaloutput$estimate[1]
        distributiondata$norm.1.sd[round] = normaloutput$estimate[2]
        distributiondata$norm.2.aic[round] = normaloutput2$aic
        distributiondata$norm.2.mean[round] = normaloutput2$estimate[1]
        distributiondata$norm.2.stdev[round] = normaloutput2$estimate[2]
        
        ##exponential
        expoutput = fitdist(dataset2$RM1.pes, "exp", keepdata = T)
        expoutput2 = fitdist(dataset3$BN1.pes, "exp", keepdata = T)
        distributiondata$exp.1.aic[round] = expoutput$aic
        distributiondata$exp.1.rate[round] = expoutput$estimate
        distributiondata$exp.2.aic[round] = expoutput2$aic
        distributiondata$exp.2.rate[round] = expoutput2$estimate
        
        ##gamma
        gammaoutput = fitdist(dataset2$RM1.pes, "gamma", lower = c(0,0), start = list(shape = 1.0, rate = 5), keepdata = T)
        gammaoutput2 = fitdist(dataset3$BN1.pes, "gamma", lower = c(0,0), start = list(shape = 1.0, rate = 5), keepdata = T)
        distributiondata$gamma.1.aic[round] = gammaoutput$aic
        distributiondata$gamma.1.shape[round] = gammaoutput$estimate[1]
        distributiondata$gamma.1.rate[round] = gammaoutput$estimate[2]
        distributiondata$gamma.2.aic[round] = gammaoutput2$aic
        distributiondata$gamma.2.shape[round] = gammaoutput2$estimate[1]
        distributiondata$gamma.2.rate[round] = gammaoutput2$estimate[2]
        
        ##log normal
        lognormoutput = fitdist(dataset2$RM1.pes, "lnorm", keepdata = T)
        lognormoutput2 = fitdist(dataset3$BN1.pes, "lnorm", keepdata = T)
        distributiondata$lnorm.1.aic[round] = lognormoutput$aic
        distributiondata$lnorm.1.mean[round] = lognormoutput$estimate[1]
        distributiondata$lnorm.1.stdev[round] = lognormoutput$estimate[2]
        distributiondata$lnorm.2.aic[round] = lognormoutput2$aic
        distributiondata$lnorm.2.mean[round] = lognormoutput2$estimate[1]
        distributiondata$lnorm.2.stdev[round] = lognormoutput2$estimate[2]
        
        ##beta
        betaoutput = fitdist(dataset2$RM1.pes, "beta", keepdata = T)
        betaoutput2 = fitdist(dataset3$BN1.pes, "beta", keepdata = T)
        distributiondata$beta.1.aic[round] = betaoutput$aic
        distributiondata$beta.1.shape1[round] = betaoutput$estimate[1]
        distributiondata$beta.1.shape2[round] = betaoutput$estimate[2]
        distributiondata$beta.2.aic[round] = betaoutput2$aic
        distributiondata$beta.2.shape1[round] = betaoutput2$estimate[1]
        distributiondata$beta.2.shape2[round] = betaoutput2$estimate[2]
        
        ##chi square
        chioutput = fitdist(dataset2$RM1.pes, "chisq", start = list(df = 1))
        chioutput2 = fitdist(dataset3$BN1.pes, "chisq", start = list(df = 1))
        distributiondata$chi.1.aic[round] = chioutput$aic
        distributiondata$chi.1.df[round] = chioutput$estimate
        distributiondata$chi.2.aic[round] = chioutput2$aic
        distributiondata$chi.2.df[round] = chioutput2$estimate
        
        ##f
        foutput = fitdist(dataset2$RM1.pes, "f", keepdata = T, 
                          start = list(df1 = (dataset$RM1.dfm[1]), df2 = (dataset$RM1.dfr[1])), 
                          optim.method="SANN")
        foutput2 = fitdist(dataset3$BN1.pes, "f", keepdata = T, 
                           start = list(df1 = (dataset$BN1.dfm[1]), df2 = (dataset$BN1.dfr[1])), 
                           optim.method="SANN")
        distributiondata$f.1.aic[round] = foutput$aic
        distributiondata$f.1.df1[round] = foutput$estimate[1]
        distributiondata$f.1.df2[round] = foutput$estimate[2]
        distributiondata$f.2.aic[round] = foutput2$aic
        distributiondata$f.2.df1[round] = foutput2$estimate[1]
        distributiondata$f.2.df2[round] = foutput2$estimate[2]        
        
        ##logistic
        logoutput = fitdist(dataset2$RM1.pes, "logis", keepdata = T)
        logoutput2 = fitdist(dataset3$BN1.pes, "logis", keepdata = T)
        distributiondata$log.1.aic[round] = logoutput$aic
        distributiondata$log.1.loc[round] = logoutput$estimate[1]
        distributiondata$log.1.scale[round] = logoutput$estimate[2]
        distributiondata$log.2.aic[round] = logoutput2$aic
        distributiondata$log.2.loc[round] = logoutput2$estimate[1]
        distributiondata$log.2.scale[round] = logoutput2$estimate[2]
        
      }
    }
  }
}

write.csv(distributiondata, "pes_distribution.csv", row.names = F)

####fes rm1 versus rm2####
round = 0
distributiondata = data.frame(N = 1:1152)

##loop a over N
Nloops = seq(20, 110, 6)
for (a in 1:length(Nloops)) {
  ##loops b over levels
  levelloop = 3:6 
  for (b in 1:length(levelloop)) {
    ##loop c over effect size
    SDloops = c(5, 3, 1)
    for (c in 1:length(SDloops)) {
      ##loop d over correlation
      corloops = c(0, .1, .3, .5, .7, .9)
      for (d in 1:length(corloops)) {
        
        dataset = subset(fulldata,
                         N == Nloops[a] &
                           levels == levelloop[b] &
                           stdev == SDloops[c] &
                           correl == corloops[d])
        
        round = round + 1
        distributiondata$N[round] = Nloops[a]
        distributiondata$levels[round] = levelloop[b]
        distributiondata$stdev[round] = SDloops[c]
        distributiondata$correl[round] = corloops[d]
        
        ##don't work with zeroes
        dataset2 = subset(dataset, RM1.fes > 0)
        dataset3 = subset(dataset, RM2.fes > 0)
        
        ##normal distribution
        normaloutput = fitdist(dataset2$RM1.fes, "norm", keepdata = T)
        normaloutput2 = fitdist(dataset3$RM2.fes, "norm", keepdata = T)
        distributiondata$norm.1.aic[round] = normaloutput$aic
        distributiondata$norm.1.mean[round] = normaloutput$estimate[1]
        distributiondata$norm.1.sd[round] = normaloutput$estimate[2]
        distributiondata$norm.2.aic[round] = normaloutput2$aic
        distributiondata$norm.2.mean[round] = normaloutput2$estimate[1]
        distributiondata$norm.2.stdev[round] = normaloutput2$estimate[2]
        
        ##exponential
        expoutput = fitdist(dataset2$RM1.fes, "exp", keepdata = T)
        expoutput2 = fitdist(dataset3$RM2.fes, "exp", keepdata = T)
        distributiondata$exp.1.aic[round] = expoutput$aic
        distributiondata$exp.1.rate[round] = expoutput$estimate
        distributiondata$exp.2.aic[round] = expoutput2$aic
        distributiondata$exp.2.rate[round] = expoutput2$estimate
        
        ##gamma
        gammaoutput = fitdist(dataset2$RM1.fes, "gamma", lower = c(0,0), start = list(shape = 1.0, rate = 5), keepdata = T)
        gammaoutput2 = fitdist(dataset3$RM2.fes, "gamma", lower = c(0,0), start = list(shape = 1.0, rate = 5), keepdata = T)
        distributiondata$gamma.1.aic[round] = gammaoutput$aic
        distributiondata$gamma.1.shape[round] = gammaoutput$estimate[1]
        distributiondata$gamma.1.rate[round] = gammaoutput$estimate[2]
        distributiondata$gamma.2.aic[round] = gammaoutput2$aic
        distributiondata$gamma.2.shape[round] = gammaoutput2$estimate[1]
        distributiondata$gamma.2.rate[round] = gammaoutput2$estimate[2]
        
        ##log normal
        lognormoutput = fitdist(dataset2$RM1.fes, "lnorm", keepdata = T)
        lognormoutput2 = fitdist(dataset3$RM2.fes, "lnorm", keepdata = T)
        distributiondata$lnorm.1.aic[round] = lognormoutput$aic
        distributiondata$lnorm.1.mean[round] = lognormoutput$estimate[1]
        distributiondata$lnorm.1.stdev[round] = lognormoutput$estimate[2]
        distributiondata$lnorm.2.aic[round] = lognormoutput2$aic
        distributiondata$lnorm.2.mean[round] = lognormoutput2$estimate[1]
        distributiondata$lnorm.2.stdev[round] = lognormoutput2$estimate[2]
        
        ##beta
        betaoutput = fitdist(dataset2$RM1.fes, "beta", keepdata = T)
        betaoutput2 = fitdist(dataset3$RM2.fes, "beta", keepdata = T)
        distributiondata$beta.1.aic[round] = betaoutput$aic
        distributiondata$beta.1.shape1[round] = betaoutput$estimate[1]
        distributiondata$beta.1.shape2[round] = betaoutput$estimate[2]
        distributiondata$beta.2.aic[round] = betaoutput2$aic
        distributiondata$beta.2.shape1[round] = betaoutput2$estimate[1]
        distributiondata$beta.2.shape2[round] = betaoutput2$estimate[2]
        
        ##chi square
        chioutput = fitdist(dataset2$RM1.fes, "chisq", start = list(df = 1))
        chioutput2 = fitdist(dataset3$RM2.fes, "chisq", start = list(df = 1))
        distributiondata$chi.1.aic[round] = chioutput$aic
        distributiondata$chi.1.df[round] = chioutput$estimate
        distributiondata$chi.2.aic[round] = chioutput2$aic
        distributiondata$chi.2.df[round] = chioutput2$estimate
        
        ##f
        foutput = fitdist(dataset2$RM1.fes, "f", keepdata = T, 
                          start = list(df1 = (dataset$RM1.dfm[1]), df2 = (dataset$RM1.dfr[1])), 
                          optim.method="SANN")
        foutput2 = fitdist(dataset3$RM2.fes, "f", keepdata = T, 
                           start = list(df1 = (dataset$RM2.dfm[1]), df2 = (dataset$RM2.dfr[1])), 
                           optim.method="SANN")
        distributiondata$f.1.aic[round] = foutput$aic
        distributiondata$f.1.df1[round] = foutput$estimate[1]
        distributiondata$f.1.df2[round] = foutput$estimate[2]
        distributiondata$f.2.aic[round] = foutput2$aic
        distributiondata$f.2.df1[round] = foutput2$estimate[1]
        distributiondata$f.2.df2[round] = foutput2$estimate[2]        
        
        ##logistic
        logoutput = fitdist(dataset2$RM1.fes, "logis", keepdata = T)
        logoutput2 = fitdist(dataset3$RM2.fes, "logis", keepdata = T)
        distributiondata$log.1.aic[round] = logoutput$aic
        distributiondata$log.1.loc[round] = logoutput$estimate[1]
        distributiondata$log.1.scale[round] = logoutput$estimate[2]
        distributiondata$log.2.aic[round] = logoutput2$aic
        distributiondata$log.2.loc[round] = logoutput2$estimate[1]
        distributiondata$log.2.scale[round] = logoutput2$estimate[2]
        
      }
    }
  }
}

write.csv(distributiondata, "fes_distribution.csv", row.names = F)

####fos rm1 versus rm2####
round = 0
distributiondata = data.frame(N = 1:1152)

##loop a over N
Nloops = seq(20, 110, 6)
for (a in 1:length(Nloops)) {
  ##loops b over levels
  levelloop = 3:6 
  for (b in 1:length(levelloop)) {
    ##loop c over effect size
    SDloops = c(5, 3, 1)
    for (c in 1:length(SDloops)) {
      ##loop d over correlation
      corloops = c(0, .1, .3, .5, .7, .9)
      for (d in 1:length(corloops)) {
        
        dataset = subset(fulldata,
                         N == Nloops[a] &
                           levels == levelloop[b] &
                           stdev == SDloops[c] &
                           correl == corloops[d])
        
        round = round + 1
        distributiondata$N[round] = Nloops[a]
        distributiondata$levels[round] = levelloop[b]
        distributiondata$stdev[round] = SDloops[c]
        distributiondata$correl[round] = corloops[d]
        
        ##don't work with zeroes
        dataset2 = subset(dataset, RM1.fos > 0)
        dataset3 = subset(dataset, RM2.fos > 0)
        
        ##normal distribution
        normaloutput = fitdist(dataset2$RM1.fos, "norm", keepdata = T)
        normaloutput2 = fitdist(dataset3$RM2.fos, "norm", keepdata = T)
        distributiondata$norm.1.aic[round] = normaloutput$aic
        distributiondata$norm.1.mean[round] = normaloutput$estimate[1]
        distributiondata$norm.1.sd[round] = normaloutput$estimate[2]
        distributiondata$norm.2.aic[round] = normaloutput2$aic
        distributiondata$norm.2.mean[round] = normaloutput2$estimate[1]
        distributiondata$norm.2.stdev[round] = normaloutput2$estimate[2]
        
        ##exponential
        expoutput = fitdist(dataset2$RM1.fos, "exp", keepdata = T)
        expoutput2 = fitdist(dataset3$RM2.fos, "exp", keepdata = T)
        distributiondata$exp.1.aic[round] = expoutput$aic
        distributiondata$exp.1.rate[round] = expoutput$estimate
        distributiondata$exp.2.aic[round] = expoutput2$aic
        distributiondata$exp.2.rate[round] = expoutput2$estimate
        
        ##gamma
        gammaoutput = fitdist(dataset2$RM1.fos, "gamma", lower = c(0,0), start = list(shape = 1.0, rate = 5), keepdata = T)
        gammaoutput2 = fitdist(dataset3$RM2.fos, "gamma", lower = c(0,0), start = list(shape = 1.0, rate = 5), keepdata = T)
        distributiondata$gamma.1.aic[round] = gammaoutput$aic
        distributiondata$gamma.1.shape[round] = gammaoutput$estimate[1]
        distributiondata$gamma.1.rate[round] = gammaoutput$estimate[2]
        distributiondata$gamma.2.aic[round] = gammaoutput2$aic
        distributiondata$gamma.2.shape[round] = gammaoutput2$estimate[1]
        distributiondata$gamma.2.rate[round] = gammaoutput2$estimate[2]
        
        ##log normal
        lognormoutput = fitdist(dataset2$RM1.fos, "lnorm", keepdata = T)
        lognormoutput2 = fitdist(dataset3$RM2.fos, "lnorm", keepdata = T)
        distributiondata$lnorm.1.aic[round] = lognormoutput$aic
        distributiondata$lnorm.1.mean[round] = lognormoutput$estimate[1]
        distributiondata$lnorm.1.stdev[round] = lognormoutput$estimate[2]
        distributiondata$lnorm.2.aic[round] = lognormoutput2$aic
        distributiondata$lnorm.2.mean[round] = lognormoutput2$estimate[1]
        distributiondata$lnorm.2.stdev[round] = lognormoutput2$estimate[2]
        
        ##beta
        betaoutput = fitdist(dataset2$RM1.fos, "beta", keepdata = T)
        betaoutput2 = fitdist(dataset3$RM2.fos, "beta", keepdata = T)
        distributiondata$beta.1.aic[round] = betaoutput$aic
        distributiondata$beta.1.shape1[round] = betaoutput$estimate[1]
        distributiondata$beta.1.shape2[round] = betaoutput$estimate[2]
        distributiondata$beta.2.aic[round] = betaoutput2$aic
        distributiondata$beta.2.shape1[round] = betaoutput2$estimate[1]
        distributiondata$beta.2.shape2[round] = betaoutput2$estimate[2]
        
        ##chi square
        chioutput = fitdist(dataset2$RM1.fos, "chisq", start = list(df = 1))
        chioutput2 = fitdist(dataset3$RM2.fos, "chisq", start = list(df = 1))
        distributiondata$chi.1.aic[round] = chioutput$aic
        distributiondata$chi.1.df[round] = chioutput$estimate
        distributiondata$chi.2.aic[round] = chioutput2$aic
        distributiondata$chi.2.df[round] = chioutput2$estimate
        
        ##f
        foutput = fitdist(dataset2$RM1.fos, "f", keepdata = T, 
                          start = list(df1 = (dataset$RM1.dfm[1]), df2 = (dataset$RM1.dfr[1])), 
                          optim.method="SANN")
        foutput2 = fitdist(dataset3$RM2.fos, "f", keepdata = T, 
                           start = list(df1 = (dataset$RM2.dfm[1]), df2 = (dataset$RM2.dfr[1])), 
                           optim.method="SANN")
        distributiondata$f.1.aic[round] = foutput$aic
        distributiondata$f.1.df1[round] = foutput$estimate[1]
        distributiondata$f.1.df2[round] = foutput$estimate[2]
        distributiondata$f.2.aic[round] = foutput2$aic
        distributiondata$f.2.df1[round] = foutput2$estimate[1]
        distributiondata$f.2.df2[round] = foutput2$estimate[2]        
        
        ##logistic
        logoutput = fitdist(dataset2$RM1.fos, "logis", keepdata = T)
        logoutput2 = fitdist(dataset3$RM2.fos, "logis", keepdata = T)
        distributiondata$log.1.aic[round] = logoutput$aic
        distributiondata$log.1.loc[round] = logoutput$estimate[1]
        distributiondata$log.1.scale[round] = logoutput$estimate[2]
        distributiondata$log.2.aic[round] = logoutput2$aic
        distributiondata$log.2.loc[round] = logoutput2$estimate[1]
        distributiondata$log.2.scale[round] = logoutput2$estimate[2]
    
      }
    }
  }
}

write.csv(distributiondata, "fos_distribution.csv", row.names = F)

####POS bn2####
round = 0
distributiondata = data.frame(N = 1:1152)

##loop a over N
Nloops = seq(20, 110, 6)
for (a in 1:length(Nloops)) {
  ##loops b over levels
  levelloop = 3:6 
  for (b in 1:length(levelloop)) {
    ##loop c over effect size
    SDloops = c(5, 3, 1)
    for (c in 1:length(SDloops)) {
      ##loop d over correlation
      corloops = c(0, .1, .3, .5, .7, .9)
      for (d in 1:length(corloops)) {
        
        dataset = subset(fulldata,
                         N == Nloops[a] &
                           levels == levelloop[b] &
                           stdev == SDloops[c] &
                           correl == corloops[d])
        
        round = round + 1
        distributiondata$N[round] = Nloops[a]
        distributiondata$levels[round] = levelloop[b]
        distributiondata$stdev[round] = SDloops[c]
        distributiondata$correl[round] = corloops[d]
        
        ##don't work with zeroes
        dataset3 = subset(dataset, BN2.pos > 0)

        ##normal distribution
        normaloutput2 = fitdist(dataset3$BN2.pos, "norm", keepdata = T)
        distributiondata$norm.2.aic[round] = normaloutput2$aic
        distributiondata$norm.2.mean[round] = normaloutput2$estimate[1]
        distributiondata$norm.2.stdev[round] = normaloutput2$estimate[2]

        ##exponential
        expoutput2 = fitdist(dataset3$BN2.pos, "exp", keepdata = T)
        distributiondata$exp.2.aic[round] = expoutput2$aic
        distributiondata$exp.2.rate[round] = expoutput2$estimate

        ##gamma
        gammaoutput2 = fitdist(dataset3$BN2.pos, "gamma", lower = c(0,0), start = list(shape = 1.0, rate = 5), keepdata = T)
        distributiondata$gamma.2.aic[round] = gammaoutput2$aic
        distributiondata$gamma.2.shape[round] = gammaoutput2$estimate[1]
        distributiondata$gamma.2.rate[round] = gammaoutput2$estimate[2]

        ##log normal
        lognormoutput2 = fitdist(dataset3$BN2.pos, "lnorm", keepdata = T)
        distributiondata$lnorm.2.aic[round] = lognormoutput2$aic
        distributiondata$lnorm.2.mean[round] = lognormoutput2$estimate[1]
        distributiondata$lnorm.2.stdev[round] = lognormoutput2$estimate[2]

        ##beta
        betaoutput2 = fitdist(dataset3$BN2.pos, "beta", keepdata = T)
        distributiondata$beta.2.aic[round] = betaoutput2$aic
        distributiondata$beta.2.shape1[round] = betaoutput2$estimate[1]
        distributiondata$beta.2.shape2[round] = betaoutput2$estimate[2]

        ##chi square
        chioutput2 = fitdist(dataset3$BN2.pos, "chisq", start = list(df = 1))
        distributiondata$chi.2.aic[round] = chioutput2$aic
        distributiondata$chi.2.df[round] = chioutput2$estimate

        ##f
        foutput2 = fitdist(dataset3$BN2.pos, "f", keepdata = T, 
                           start = list(df1 = (dataset$BN2.dfm[1]), df2 = (dataset$BN2.dfr[1])), 
                           optim.method="SANN")
        distributiondata$f.2.aic[round] = foutput2$aic
        distributiondata$f.2.df1[round] = foutput2$estimate[1]
        distributiondata$f.2.df2[round] = foutput2$estimate[2]        

        ##logistic
        #logoutput2 = fitdist(dataset3$BN2.pos, "logis", keepdata = T)
        #distributiondata$log.2.aic[round] = logoutput2$aic
        #distributiondata$log.2.loc[round] = logoutput2$estimate[1]
        #distributiondata$log.2.scale[round] = logoutput2$estimate[2]

      }
    }
  }
}

write.csv(distributiondata, "pos_distribution.csv", row.names = F)

```

```{r examine-dist}

##import distribution data
FESdist = read.csv("fes_distribution.csv")
FOSdist = read.csv("fos_distribution.csv")
PESdist = read.csv("pes_distribution.csv")
POSdist = read.csv("pos_distribution.csv")
GESdist = read.csv("ges_distribution.csv")

##examine the types of distributions most commonly picked
aiccolumns1 = c("norm.1.aic", "exp.1.aic", "gamma.1.aic", "lnorm.1.aic", 
                "beta.1.aic", "chi.1.aic", "f.1.aic", "log.1.aic")
aiccolumns2 = c("norm.2.aic", "exp.2.aic", "gamma.2.aic", "lnorm.2.aic",
                "beta.2.aic", "chi.2.aic", "f.2.aic", "log.2.aic")

####fes information####
##calculate for first estimate
temp = FESdist[ , aiccolumns1]
table(colnames(temp)[apply(temp,1,which.min)])
FESdist$smallest1 = colnames(temp)[apply(temp,1,which.min)]

##calculate for the second estimate
temp = FESdist[ , aiccolumns2]
table(colnames(temp)[apply(temp,1,which.min)])
FESdist$smallest2 = colnames(temp)[apply(temp,1,which.min)]

with(FESdist, table(smallest1, N))
with(FESdist, table(smallest1, stdev))
with(FESdist, table(smallest1, correl))
with(FESdist, table(smallest1, levels))

with(FESdist, table(smallest2, N))
with(FESdist, table(smallest2, stdev))
with(FESdist, table(smallest2, correl))
with(FESdist, table(smallest2, levels))

####fos information####
##calculate for first estimate
temp = FOSdist[ , aiccolumns1]
table(colnames(temp)[apply(temp,1,which.min)])
FOSdist$smallest1 = colnames(temp)[apply(temp,1,which.min)]

##calculate for the second estimate
temp = FOSdist[ , aiccolumns2]
table(colnames(temp)[apply(temp,1,which.min)])
FOSdist$smallest2 = colnames(temp)[apply(temp,1,which.min)]

with(FOSdist, table(smallest1, N))
with(FOSdist, table(smallest1, stdev))
with(FOSdist, table(smallest1, correl))
with(FOSdist, table(smallest1, levels))

with(FOSdist, table(smallest2, N))
with(FOSdist, table(smallest2, stdev))
with(FOSdist, table(smallest2, correl))
with(FOSdist, table(smallest2, levels))

####ges information####
##calculate for first estimate
temp = GESdist[ , aiccolumns1]
table(colnames(temp)[apply(temp,1,which.min)])
GESdist$smallest1 = colnames(temp)[apply(temp,1,which.min)]

##calculate for the second estimate
temp = GESdist[ , aiccolumns2]
table(colnames(temp)[apply(temp,1,which.min)])
GESdist$smallest2 = colnames(temp)[apply(temp,1,which.min)]

with(GESdist, table(smallest1, N))
with(GESdist, table(smallest1, stdev))
with(GESdist, table(smallest1, correl))
with(GESdist, table(smallest1, levels))

with(GESdist, table(smallest2, N))
with(GESdist, table(smallest2, stdev))
with(GESdist, table(smallest2, correl))
with(GESdist, table(smallest2, levels))

####pes information####
##calculate for first estimate
temp = PESdist[ , aiccolumns1]
table(colnames(temp)[apply(temp,1,which.min)])
PESdist$smallest1 = colnames(temp)[apply(temp,1,which.min)]

##calculate for the second estimate
temp = PESdist[ , aiccolumns2]
table(colnames(temp)[apply(temp,1,which.min)])
PESdist$smallest2 = colnames(temp)[apply(temp,1,which.min)]

with(PESdist, table(smallest1, N))
with(PESdist, table(smallest1, stdev))
with(PESdist, table(smallest1, correl))
with(PESdist, table(smallest1, levels))

with(PESdist, table(smallest2, N))
with(PESdist, table(smallest2, stdev))
with(PESdist, table(smallest2, correl))
with(PESdist, table(smallest2, levels))

####POS information####
##calculate for the second estimate
temp = POSdist[ , aiccolumns2[-length(aiccolumns2)]]
table(colnames(temp)[apply(temp,1,which.min)])
POSdist$smallest2 = colnames(temp)[apply(temp,1,which.min)]

with(POSdist, table(smallest2, N))
with(POSdist, table(smallest2, stdev))
with(POSdist, table(smallest2, correl))
with(POSdist, table(smallest2, levels))
```

```{r nc-dist}
compdist = matrix(NA, nrow = 1152, ncol = 9)
compdist = as.data.frame(compdist)
colnames(compdist) = c("Type", "N", "levels", "stdev", "correl", "fcs", "fnccs", "bcs", "bnccs")
####GES RM1####
simnum = 0

Nloops = seq(20, 111, 6)
for (a in 1:length(Nloops)) {
  levelloop = 3:6 

  for (b in 1:length(levelloop)) {
    SDloops = c(5, 3, 1)

    for (c in 1:length(SDloops)) {
      corloops = c(0, .1, .3, .5, .7, .9)

      for (d in 1:length(corloops)) {
        
        simnum = simnum + 1

        tempdata = subset(fulldata, 
                          N == Nloops[a] & stdev == SDloops[c] & correl == corloops[d] & levels == levelloop[b])
        CP = seq(min(tempdata$RM1.ges), max(tempdata$RM1.ges), .05)
        pfraw = NA
        pfrawnc = NA
        betaraw = NA
        betarawnc = NA
        bin = NA

        for (i in 1:length(CP)) {
          
          ##calculate the values for f
          pfraw[i] = pf(CP[i], df1 = mean(tempdata$RM1.dfm), df2 = mean(tempdata$RM1.dfr))
          
          ##calculate the frequency of values you would expect from noncentral F
          pfrawnc[i] = pf(CP[i], df1 = mean(tempdata$RM1.dfm), df2 = mean(tempdata$RM1.dfr), ncp = mean(tempdata$ncp))
          
          ##calculate the frequency of values you would expect from beta
          GEStemp = subset(GESdist, 
                           N == Nloops[a] & stdev == SDloops[c] & correl == corloops[d] & levels == levelloop[b])
          betaraw[i] = pbeta(CP[i], shape1 = GEStemp$beta.1.shape1, shape2 = GEStemp$beta.1.shape2)
          
          ##calculate noncentral beta
          betarawnc[i] = pbeta(CP[i], shape1 = GEStemp$beta.1.shape1, 
                               shape2 = GEStemp$beta.1.shape2, ncp = mean(tempdata$ncp))
          
          bin[i] = sum(as.numeric(tempdata$RM1.ges < CP[i]))
          
        }

        ##convert to frequency 
        samplesize = length(tempdata)
        last = length(pfraw)
        freqf = (c(pfraw[-1],0) - pfraw)[-last] * samplesize
        freqfnc = (c(pfrawnc[-1],0) - pfrawnc)[-last] * samplesize
        freqb = (c(betaraw[-1],0) - betaraw)[-last] * samplesize
        freqbnc = (c(betarawnc[-1],0) - betarawnc)[-last] * samplesize
        freqreal = (c(bin[-1],0) - bin)[-last]
        
        ##compare to the actual distribution
        compdist$Type[simnum] = "RM1.ges"
        compdist$N[simnum] = Nloops[a]
        compdist$levels[simnum] = levelloop[b]
        compdist$stdev[simnum] = SDloops[c]
        compdist$correl[simnum] = corloops[d]
        compdist$fcs[simnum] = sum((freqreal - freqf)^2 / freqf)
        compdist$fnccs[simnum] = sum((freqreal - freqfnc)^2 / freqfnc)
        compdist$bcs[simnum] = sum((freqreal - freqb)^2 / freqb)
        compdist$bnccs[simnum] = sum((freqreal - freqbnc)^2 / freqbnc)
      }
    }
  }
}
```

```{r dist-graph}
examplelarge = subset(largedata, levels == 4)
normalmean = PESdist$norm.1.mean[PESdist$levels == 4 & PESdist$correl == 0 & PESdist$stdev == 1 & PESdist$N == 110]
normalsd = PESdist$norm.1.sd[PESdist$levels == 4 & PESdist$correl == 0 & PESdist$stdev == 1 & PESdist$N == 110]
beta1 = PESdist$beta.1.shape1[PESdist$levels == 4 & PESdist$correl == 0 & PESdist$stdev == 1 & PESdist$N == 110]
beta2 = PESdist$beta.1.shape2[PESdist$levels == 4 & PESdist$correl == 0 & PESdist$stdev == 1 & PESdist$N == 110]
gshape = PESdist$gamma.1.shape[PESdist$levels == 4 & PESdist$correl == 0 & PESdist$stdev == 1 & PESdist$N == 110]
grate = PESdist$gamma.1.rate[PESdist$levels == 4 & PESdist$correl == 0 & PESdist$stdev == 1 & PESdist$N == 110]

binsize = .005
samplesize = 1000

CP = seq(min(examplelarge$RM1.pes), max(examplelarge$RM1.pes), .005)
##calculate the values for f
pfraw = pf(CP, df1 = mean(examplelarge$RM1.dfm), df2 = mean(examplelarge$RM1.dfr))

##calculate the frequency of values you would expect from noncentral F
pfrawnc = pf(CP, df1 = mean(examplelarge$RM1.dfm), df2 = mean(examplelarge$RM1.dfr), ncp = mean(examplelarge$ncp))
          
##calculate the frequency of values you would expect from beta
betaraw = pbeta(CP, shape1 = beta1, shape2 = beta2)

##calculate the frequency of values you would expect from normal
normalraw = pnorm(CP, mean = normalmean, sd = normalsd)

##calculate the frequency of values you would expect from gamma
gammaraw = pgamma(CP, shape = gshape, rate = grate)

for (i in 1:length(CP)){
  bin[i] = sum(as.numeric(examplelarge$RM1.pes < CP[i]))
  }

last = length(pfraw)
freqf = (c(pfraw[-1],0) - pfraw)[-last] * samplesize
freqfnc = (c(pfrawnc[-1],0) - pfrawnc)[-last] * samplesize
freqb = (c(betaraw[-1],0) - betaraw)[-last] * samplesize
freqnorm = (c(normalraw[-1],0) - normalraw)[-last] * samplesize
freqgamma = (c(gammaraw[-1],0) - gammaraw)[-last] * samplesize
freqreal = (c(bin[-1],0) - bin)[-last]

CP1 = CP[-1]
freqdata = cbind.data.frame("freqf1" = freqf,"freqfnc1" = freqfnc,
                            "freqb1" = freqb, CP1, "freqnorm1" = freqnorm, 
                            "freqgamma1" = freqgamma, "freqreal1" = freqreal)   
  
distgraph = ggplot(freqdata, aes(CP1, freqreal)) +
    geom_line(data = freqdata, aes(x = CP1, y = freqreal1), color = "red", linetype = "solid") +
    geom_line(data = freqdata, aes(x = CP1, y = freqb1), linetype = "dashed") + 
    geom_line(data = freqdata, aes(x = CP1, y = freqfnc1), linetype = "dotted") +
    geom_line(data = freqdata, aes(x = CP1, y = freqnorm1), linetype = "dotdash") +
    geom_line(data = freqdata, aes(x = CP1, y = freqgamma1), linetype = "longdash") +  
    cleanup +
    xlab("Partial Eta Squared") + 
    ylab("Frequency") +
    annotate("text", x = .19, y = 60, label = "  Gamma", hjust = 0) +
    annotate("text", x = .19, y = 56, label = "-- Beta", hjust = 0) +
    annotate("text", x = .19, y = 52, label = "-. Normal", hjust = 0) +
    annotate("text", x = .19, y = 48, label = ".. F", hjust = 0) +
    annotate("text", x = .19, y = 44, label = "Observed", hjust = 0, color = "red")

tiff(filename = "distgraph.tiff", res = 300, width = 6, 
     height = 6, units = 'in', compression = "lzw")
plot(distgraph)
dev.off()    
  
    
  
```

```{r confidenceintervals}
CItest = matrix(NA, nrow = 1152, ncol = 31)
colnames(CItest) = c("LLges.RM1", "ULges.RM1", "LLges.RM2", "ULges.RM2", 
                     "ges.RM1.mean", "ges.RM2.mean",
                     "LLfos.RM1", "ULfos.RM1", "LLfos.RM2", "ULfos.RM2",
                     "fos.RM1.mean", "fos.RM2.mean",
                     "LLpes.RM1", "ULpes.RM1", "LLpes.RM2", "ULpes.RM2",
                     "pes.RM1.mean", "pes.RM2.mean",
                     "LLfes.RM1", "ULfes.RM1", "LLfes.RM2", "ULfes.RM2",
                     "fes.RM1.mean", "fes.RM2.mean",
                     "LLpos.BN2", "ULpos.BN2", "pos.BN2.mean",
                     "N", "levels", "correl", "stdev")

CItest = as.data.frame(CItest)
i = 1

Nloops = seq(20, 111, 6)
for (a in 1:length(Nloops)) {
  levelloop = 3:6 

  for (b in 1:length(levelloop)) {
    SDloops = c(5, 3, 1)

    for (c in 1:length(SDloops)) {
      corloops = c(0, .1, .3, .5, .7, .9)

      for (d in 1:length(corloops)) {
        
        tempdata = subset(fulldata, N == Nloops[a] & 
                            stdev == SDloops[c] & 
                            correl == corloops[d] & 
                            levels == levelloop[b])
        
        CItest$N[i] = Nloops[a]
        CItest$levels[i] = levelloop[b]
        CItest$correl[i] = corloops[d]
        CItest$stdev[i] = SDloops[c]
        
        CItest$LLges.RM1[i] = quantile(tempdata$RM1.ges, probs = c(0.025,0.975))[1]
        CItest$ULges.RM1[i] = quantile(tempdata$RM1.ges, probs = c(0.025,0.975))[2]
        CItest$LLges.RM2[i] = quantile(tempdata$RM2.ges, probs = c(0.025,0.975))[1]
        CItest$ULges.RM2[i] = quantile(tempdata$RM2.ges, probs = c(0.025,0.975))[2]
        CItest$ges.RM1.mean[i] = mean(tempdata$RM1.ges)
        CItest$ges.RM2.mean[i] = mean(tempdata$RM2.ges)
        
        CItest$LLfos.RM1[i] = quantile(tempdata$RM1.fos, probs = c(0.025,0.975))[1]
        CItest$ULfos.RM1[i] = quantile(tempdata$RM1.fos, probs = c(0.025,0.975))[2]
        CItest$LLfos.RM2[i] = quantile(tempdata$RM2.fos, probs = c(0.025,0.975))[1]
        CItest$ULfos.RM2[i] = quantile(tempdata$RM2.fos, probs = c(0.025,0.975))[2]
        CItest$fos.RM1.mean[i] = mean(tempdata$RM1.fos)
        CItest$fos.RM2.mean[i] = mean(tempdata$RM2.fos)
        
        CItest$LLfes.RM1[i] = quantile(tempdata$RM1.fes, probs = c(0.025,0.975))[1]
        CItest$ULfes.RM1[i] = quantile(tempdata$RM1.fes, probs = c(0.025,0.975))[2]
        CItest$LLfes.RM2[i] = quantile(tempdata$RM2.fes, probs = c(0.025,0.975))[1]
        CItest$ULfes.RM2[i] = quantile(tempdata$RM2.fes, probs = c(0.025,0.975))[2]
        CItest$fes.RM1.mean[i] = mean(tempdata$RM1.fes)
        CItest$fes.RM2.mean[i] = mean(tempdata$RM2.fes)
        
        CItest$LLpes.RM1[i] = quantile(tempdata$RM1.pes, probs = c(0.025,0.975))[1]
        CItest$ULpes.RM1[i] = quantile(tempdata$RM1.pes, probs = c(0.025,0.975))[2]
        CItest$LLpes.RM2[i] = quantile(tempdata$RM2.pes, probs = c(0.025,0.975))[1]
        CItest$ULpes.RM2[i] = quantile(tempdata$RM2.pes, probs = c(0.025,0.975))[2]
        CItest$pes.RM1.mean[i] = mean(tempdata$RM1.pes)
        CItest$pes.RM2.mean[i] = mean(tempdata$RM2.pes)
        
        CItest$LLpos.BN2[i] = quantile(tempdata$BN2.pos, probs = c(0.025,0.975))[1]
        CItest$ULpos.BN2[i] = quantile(tempdata$BN2.pos, probs = c(0.025,0.975))[2]
        CItest$pos.BN2.mean[i] = mean(tempdata$BN2.pos)
        
        i = i + 1
 
        
      } #close corloop
    } #close sd loop
  } #close level loop
} #close N loop

library(MBESS)
library(psychometric)


for (i in 1:nrow(CItest))
{

  #stuff = ci.R2(R2 = CItest$ges.RM1.mean[i], 
  #                      df.1 = (CItest$levels[i]-1), 
  #                      df.2 = (CItest$levels[i]-1)*(CItest$N[i]-1))  
  #stuff2 = CI.Rsq(CItest$ges.RM1.mean[i], CItest$N[i], CItest$levels[i], level = 0.95)
  #CItest$LLNC.ges.RM1[i] = stuff$Lower.Conf.Limit.R2
  #CItest$ULNC.ges.RM1[i] = stuff$Upper.Conf.Limit.R2
  #CItest$LLC.ges.RM1[i] = stuff2$LCL
  #CItest$ULC.ges.RM1[i] = stuff2$UCL
  
  stuff = ci.R2(R2 = CItest$pes.RM1.mean[i], 
                        df.1 = (CItest$levels[i]-1), 
                        df.2 = (CItest$levels[i]-1)*(CItest$N[i]-1))  
  stuff2 = CI.Rsq(CItest$pes.RM1.mean[i], CItest$N[i], CItest$levels[i], level = 0.95)
  CItest$LLNC.pes.RM1[i] = stuff$Lower.Conf.Limit.R2
  CItest$ULNC.pes.RM1[i] = stuff$Upper.Conf.Limit.R2
  CItest$LLC.pes.RM1[i] = stuff2$LCL
  CItest$ULC.pes.RM1[i] = stuff2$UCL
  
  z.pes.RM1 = 0.5*log((1+sqrt(CItest$pes.RM1.mean[i]))/(1-sqrt(CItest$pes.RM1.mean[i])))
  se.z.pes.RM1 = 1 / sqrt(CItest$N[i] - 3)
  CItest$LLZ.pes.RM1[i] = tanh(z.pes.RM1 - se.z.pes.RM1*qnorm(.025, lower.tail = F))^2
  CItest$ULZ.pes.RM1[i] = tanh(z.pes.RM1 + se.z.pes.RM1*qnorm(.025, lower.tail = F))^2
}

#CItest$LLC.ges.RM1[CItest$LLC.ges.RM1 < 0] = 0
#CItest$LLNC.ges.RM1[CItest$LLNC.ges.RM1 < 0] = 0
CItest$LLC.pes.RM1[CItest$LLC.pes.RM1 < 0] = 0
CItest$LLNC.pes.RM1[CItest$LLNC.pes.RM1 < 0] = 0

##poster stuff
##temp drop N levels
CItest = subset(CItest, N == 26 | N == 50 | N == 104)
round(tapply(CItest$LLpes.RM1, list(CItest$N, CItest$stdev), mean),3)
round(tapply(CItest$ULpes.RM1, list(CItest$N, CItest$stdev), mean),3)

round(tapply(CItest$LLpes.RM1, list(CItest$N, CItest$stdev), mean),3) - round(tapply(CItest$LLNC.pes.RM1, list(CItest$N, CItest$stdev), mean),3)

round(tapply(CItest$ULpes.RM1, list(CItest$N, CItest$stdev), mean),3) - round(tapply(CItest$ULNC.pes.RM1, list(CItest$N, CItest$stdev), mean),3)

round(tapply(CItest$LLpes.RM1, list(CItest$N, CItest$stdev), mean),3) - round(tapply(CItest$LLC.pes.RM1, list(CItest$N, CItest$stdev), mean),3)

round(tapply(CItest$ULpes.RM1, list(CItest$N, CItest$stdev), mean),3) - round(tapply(CItest$ULC.pes.RM1, list(CItest$N, CItest$stdev), mean),3)

round(tapply(CItest$LLpes.RM1, list(CItest$N, CItest$stdev), mean),3) - 
round(tapply(CItest$LLZ.pes.RM1, list(CItest$N, CItest$stdev), mean),3)

round(tapply(CItest$ULpes.RM1, list(CItest$N, CItest$stdev), mean),3) - round(tapply(CItest$ULZ.pes.RM1, list(CItest$N, CItest$stdev), mean),3)
```

# Results

## Distribution Estimation
- talk about the distributions here

## Sampling Variance
- john! do the thing here where you talk about the meta stuff you did i have zero clue about it. 

## Confidence Intervals
- I will talk here about how to create confidence intervals what we tested against and why we should use this MOTE/MBESS estimator. 

# Discussion


\newpage

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
